\documentclass[a4paper]{article}

\usepackage{hyperref}
\hypersetup{colorlinks,citecolor=,urlcolor=,linkcolor=}

\usepackage{natbib}
\usepackage{bibentry}
\nobibliography*

\newcommand{\bibpara}[1]{\paragraph{\cite{#1}}\bibentry{#1}\par}

\hyphenation{
Schall-feld-syn-the-se
}

\title{Wave Field Synthesis -- Some Literature}
\author{Matthias Geier}
\date{}

\begin{document}
\maketitle

\begin{abstract}
A (more or less) chronological (and very incomplete) list of references with
some (of course totally biased) comments.
In the end there is the same list sorted by author.
In between there are some links to some open-source software which can do WFS.

All this is work-in-progress!

If you find errors or omissions, please create an
issue or a pull request: \url{https://github.com/mgeier/literature-review}
\end{abstract}

\bibpara{berkhout1988holographic}

\bibpara{berkhout1993wfs}

\bibpara{vogel1993wfs}

\bibpara{start1997wfs}

\bibpara{verheijen1998wfs}

\bibpara{labeeuw1998optimization}

\bibpara{sonke2000variable}

\bibpara{wittek2002opsi}

\bibpara{hulsebos2004auralization}

\bibpara{apel2004equalization}

\bibpara{melchior2005ar}

\bibpara{springer2006stereo_displays}
WFS combined with VR. Two people are tracked with an optical tracking system.
Stereoscopic shutter glasses.

\bibpara{corteel2006equalization}

\bibpara{corteel2007directional}

\bibpara{spors2007selection}

\bibpara{ahrens2007directional}

\bibpara{spors2008wfs}

\bibpara{melchior2008optimization}
Tracked (single) user position, source directivity, room simulation.
3 optimizations: secondary source selection, delay correction, amplitude
correction.
Pilot study: ``improved localization and sound quality for focused sources''.
2 experiments:
one with walking around a focused source and
the other with 8
plane waves to find out if amplitudes are evenly distributed(``perceived
diffuseness'').
Extension to more than one listener, ``center of gravity'', only works if
listeners are close together.

\bibpara{leslie2009installations}
Optically tracked input devices plus Wiimote.

\bibpara{spors2009focused}

\bibpara{spors2010prefilter}
Thorough discussion of the pre-equalization filter used to efficiently implement
WFS.
Derivation by means of the Spectral Division Method (SDM).
Only non-focused point sources and plane waves are considered.
Only linear loudspeaker arrays are considered.

\bibpara{wierstorf2012localization}

\bibpara{ahrens2012analytic}

\bibpara{blauert2012synopsis}
Nice overview about loudspeaker-based techniques like HOA, VBAP, WFS, DirAC, ...

\bibpara{fohl2013gesture}

\section*{Open-Source Software for WFS}

This is roughly sorted chronologically and surely incomplete.

\subsection*{WONDER}

\url{http://sourceforge.net/projects/swonder/}\\
\url{https://github.com/davezerave/wonder/}

\bibpara{baalman2004wonder}
\bibpara{baalman2005updates}
\bibpara{baalman2006swonder3dq}
\bibpara{baalman2007renewed}

\subsection*{WFSCollider}

\url{https://github.com/GameOfLife/WFSCollider/}\\
\url{http://sourceforge.net/projects/wfscollider/}\\
\url{http://gameoflife.nl/en}

since 2006?

\subsection*{WFSynth}

\url{http://wfsynth.sourceforge.net/}

\bibpara{wolcott2007wfs}

\subsection*{SoundScape Renderer (SSR)}

\url{http://spatialaudio.net/ssr/}\\
\url{https://github.com/SoundScapeRenderer/ssr/}

Development since 2006, first public release in 2010.

\bibpara{geier2008ssr}
\bibpara{geier2012ssr}

\subsection*{WFS Designer}

\url{http://www.mattmontag.com/projects-page/wfs-designer}\\
\url{https://github.com/mmontag/WFS-Designer}

\bibpara{montag2011wfs}

\bibliographystyle{plainnat}
\bibliography{wfs}

\end{document}

% vim:textwidth=80
